### 2014-09-22 paper.tex
Start of the processed data section.

>>>>

\section{Processed Data}

We developed a command line data processing tool for common gait computations
and provide the processed data from this. The tool is centered around two main
classes, one to store a complete trial in memory and a second to compute common
gait variables of interest.

The \verb|motek.DFlowData| class stores all the data presented in the previous
section and encodes several ``cleaning'' operations to put the data into a
usable form.

\begin{itemize}
  \item Loads the meta data file into a Python dictionary.
  \item Loads the DFlow mocap module TSV file into Pandas \verb|DataFrame|.
  \item Relabels the column headers to more meaningful names if this is
    specified in the meta data.
  \item Identifies the missing values in the mocap marker data and replaces
    them with \verb|numpy.nan|.
  \item Interpolates the missing marker values and replaces them with
    interpolated estimates.
  \item Loads the DFlow record moudle TSV file into a Pandas \verb|DataFrame|.
  \item Extracts the events and creates a dictionary mapping the event names in
    the meta data to the events detected in the record module file.
  \item Merges the data from the mocap module and record module into one data
    frame at the maximum common constant sample rate.
  \item Extracts sections of the data bounded by the events.
  \item Saves the cleaned data to disk.
\end{itemize}

The \verb|gait.WalkingData| class is then used to compute things such as gait
landmarks (toe off and heel strike times), basic 2D inverse dynamics, and to
store the data into a Pandas \verb|Panel| with each gait cycle on the main axis
at a specified sample rate. This data is also saved to disk in HDF5 format.
